---
title: "Code-appendix Example"
format: pdf
filters:
  - code-appendix
code-appendix-title: "Source Code:"
code-appendix-header-level: 2
code-appendix-file: code-appendix.r
code-appendix-write: true
---

This filter moves the source code generating the following text

```{r}
to_end <- "move source code to an appendix please, thx"

to_end
```

as well as this table

```{r}
knitr::kable(data.frame(X = 1:3, Y = letters[1:3]))
```


to an appendix at the end of the document, (but keeps the output in its usual place).
Force a page break in the `.qmd` to display appendix on separate page. Note that 
you can change the appendix header using the `code-appendix-title` and 
`code-appendix-header-level` options in the document YAML. 

To write the source code to a file, set `code-appendix-file:` to a string pointing to
the file you would like to write to. Include file paths (relative to `.qmd`) and
file extensions (defaults to `.md`). In this example, `code-appendix-file: code-appendix.r`
tells the filter to write the source code generating the above text and table
to an executable `.r` file. The automatic creation of the appendix can be turned
off with `code-appendix-write: false` if you would like to just write the source 
to a file.

{{< pagebreak >}}

